The introduction of ggplot2
========================================================

scatter point:

```{r}
library(ggplot2)
library(reshape2)
library(plyr)
head(iris)
```

plot a scatter plot with Sepal.Length as x axis and Sepal.Width as y axis, for example:

```{r fig.width=7, fig.height=6}
a <- ggplot(data = iris, aes(x=Sepal.Length, y=Sepal.Width)) + geom_point()
a
# change the size of points
b <-ggplot(data = iris, aes(x=Sepal.Length, y=Sepal.Width)) + geom_point(size=3)
b
#change the color of points
c <-ggplot(data = iris, aes(x=Sepal.Length, y=Sepal.Width, colour=Species)) + geom_point()
c
#change the shape of points according to species of flowers
d <-ggplot(data = iris, aes(x=Sepal.Length, y=Sepal.Width, colour=Species)) + geom_point(aes(shape=Species), size=3)
d
```

more examples with diamonds data, we want to show some figures fast so to reduce the data size and improve the speed

```{r}
d2 <- diamonds[sample(1:dim(diamonds)[1], 1000), ]
ggplot(data = d2, aes(x = carat, y = price, color = color)) + geom_point() + theme_gray()
```

boxplot figure with birthwt that from MASS package

```{r}
library(MASS)
ggplot(data=birthwt, aes(x=factor(race), y=bwt)) + geom_boxplot()
```

histogram figure with faithfull data

```{r,fig.width=8,fig.height=6,comment=F}
ggplot(faithful, aes(x=waiting)) + geom_histogram(binwidth=8,colour="black",fill="steelblue")
```

line figure with climate data from gcookbook
```{r,fig.width=10,fig.height=8}
library(gcookbook)
a <- ggplot(data=climate, aes(x=Year, y=Anomaly10y)) + geom_line()
a 
b <- ggplot(data=climate, aes(x=Year, y=Anomaly10y)) + geom_ribbon(aes(ymin=Anomaly10y-Unc10y, ymax=Anomaly10y+Unc10y), fill="blue",alpha=.1) + geom_line(color="steelblue")
b
cplot <- ggplot(climate, aes(Year, Anomaly10y))
cplot <- cplot + geom_line(size = 0.7, color = "black")
cplot <- cplot + geom_line(aes(Year, Anomaly10y + Unc10y), linetype = "dashed", size = 0.7, color = "red")
cplot <- cplot + geom_line(aes(Year, Anomaly10y - Unc10y), linetype = "dashed", size = 0.7, color = "red")
cplot + theme_gray()
```

bar plot with iris data
```{r}
ggplot(iris, aes(Species, Sepal.Length)) + geom_bar(stat = "identity")
df <- melt(iris, id.vars="Species")
bar_stat <- ggplot(data=df, aes(x=Species, y=value, fill=variable)) + geom_bar(stat="identity", position="dodge")
bar_stat + coord_flip()

color_try <- ggplot(df, aes(Species, value, fill = variable)) + geom_bar(stat = "identity", position = "dodge") + scale_fill_manual(values=c("red","blue","green","yellow")) + facet_wrap(~Species)
color_try
color_try2<- ggplot(df, aes(Species, value, fill = variable)) + geom_bar(stat = "identity", position = "dodge") + scale_fill_manual(values=c("red","blue","green","yellow")) + facet_grid(Species~.)
color_try2
color_try3<- ggplot(df, aes(Species, value, fill = variable)) + geom_bar(stat = "identity", position = "dodge") + scale_fill_manual(values=c("red","blue","green","yellow")) + facet_grid(.~Species)
color_try3
```

add some statistical result to the figure
```{r}
ggplot(data=iris, aes(x=Sepal.Length, y=Sepal.Width, colour=Species)) + geom_point(aes(shape=Species), size=3) + geom_smooth(method="lm") + facet_grid(Species~.)
```

modify the theme of ggplot2
```{r}
defa <- ggplot(iris, aes(Sepal.Length, Sepal.Width, color = Species)) + geom_point(size = 1.2, shape = 16) + facet_wrap( ~ Species) + theme()
defa
lk <- ggplot(iris, aes(Sepal.Length, Sepal.Width, color = Species)) + geom_point(size = 1.2, shape = 16) + facet_wrap( ~ Species) + theme(legend.key=element_rect(fill=NA))
lk
ld <- lk + theme(legend.position="bottom")
ld
lz <- ld + theme(strip.background=element_rect(fill=NA))
lz
lw <- lz + theme(axis.title.y=element_text(angle=30))
lw
lline <- lw + theme(panel.grid.major=element_line(color="black",linetype="dashed"), panel.grid.minor=element_line(color="grey",linetype="dashed"))
lline
```




